CKY Parsing With Independence Constraints

### 2015-07-14 paper/paper.tex
Move files for paper to subdirectory

\title{CKY Parsing With Independence Constraints}
\author{Joseph Irwin \\
  Graduate School of Information Science\hspace{1em} \\
  Nara Institute of Science and Technology\hspace{1em} \\
  {\tt joseph-i@is.naist.jp} \\\And
  Yuji Matsumoto \\
  Graduate School of Information Science \\
  Nara Institute of Science and Technology \\
  {\tt matsu@is.naist.jp} \\}

>>>>

\title{CKY Parsing With Independence Constraints}
\author{Joseph Irwin \\
  Graduate School of Information Science\hspace{1em} \\
  Nara Institute of Science and Technology\hspace{1em} \\
  Nara, Japan \hspace{1em} \\
  {\tt joseph-i@is.naist.jp} \\\And
  Yuji Matsumoto \\
  Graduate School of Information Science \\
  Nara Institute of Science and Technology \\
  Nara, Japan \hspace{1em} \\
  {\tt matsu@is.naist.jp} \\}
